---
title: "BankCamp"
author: "Group 4: Andrew Rizk, Dominik Thausing, Andrea Salvati, Aksel Husebø, Manuel Ehmann, Daan Pelt, Martin Da Costa Louzada"
date: "3 June 2019"
output:
  html_document:
    fig_caption: yes
    fig_width: 6
    fig_height: 4
    toc: yes
    toc_float: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Bank Marketing
Abstract: The data is related with direct marketing campaigns (phone calls) of a Portuguese banking institution. The classification goal is to predict if the client will subscribe a term deposit (variable y).

Data Set Information: The data is related with direct marketing campaigns of a Portuguese banking institution. The marketing campaigns were based on phone calls. Often, more than one contact to the same client was required, in order to access if the product (bank term deposit) would be ('yes') or not ('no') subscribed.

#### Attribute Information:

##### Bank client data:
1 - age (numeric)
2 - job : type of job (categorical: 'admin.','blue-collar','entrepreneur','housemaid','management','retired','self-employed','services','student','technician','unemployed','unknown')
3 - marital : marital status (categorical: 'divorced','married','single','unknown'; note: 'divorced' means divorced or widowed)
4 - education (categorical: 'basic.4y','basic.6y','basic.9y','high.school','illiterate','professional.course','university.degree','unknown')
5 - default: has credit in default? (categorical: 'no','yes','unknown')
6 - housing: has housing loan? (categorical: 'no','yes','unknown')
7 - loan: has personal loan? (categorical: 'no','yes','unknown')

##### related with the last contact of the current campaign:
8 - contact: contact communication type (categorical: 'cellular','telephone') 
9 - month: last contact month of year (categorical: 'jan', 'feb', 'mar', ..., 'nov', 'dec')
10 - day_of_week: last contact day of the week (categorical: 'mon','tue','wed','thu','fri')
11 - duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if duration=0 then y='no'). Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input should only be included for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.

##### other attributes:
12 - campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)
13 - pdays: number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously contacted)
14 - previous: number of contacts performed before this campaign and for this client (numeric)
15 - poutcome: outcome of the previous marketing campaign (categorical: 'failure','nonexistent','success')

##### social and economic context attributes
16 - emp.var.rate: employment variation rate - quarterly indicator (numeric)
17 - cons.price.idx: consumer price index - monthly indicator (numeric) 
18 - cons.conf.idx: consumer confidence index - monthly indicator (numeric) 
19 - euribor3m: euribor 3 month rate - daily indicator (numeric)
20 - nr.employed: number of employees - quarterly indicator (numeric)

##### Output variable (desired target):
21 - y - has the client subscribed a term deposit? (binary: 'yes','no')

##### Source:
Dataset from : http://archive.ics.uci.edu/ml/datasets/Bank+Marketing#

#### Load Libraries
```{r Libraries to be used for this project, warning=FALSE}
library(data.table)
library(dplyr)
library(DataExplorer)
library(ggplot2)
library(tidyr)
library(dplyr)    
library(png)      
library(knitr)     
library(moments)   
library(e1071)     
library(glmnet)    
library(caret)     
library(corrplot)
library(ggloop)
library(leaflet)
library(RColorBrewer)
library(devtools)
```

#### Load Datasets
```{r Datasets}
bank_train <- read.csv("BankCamp_train.csv", header = T)
bank_test <- read.csv("BankCamp_test.csv", header = T)

# Since the test set has no target column, we will create one before combining both
bank_test$y <- NA

# We will add a column with a factor of train/test to help with the dataset splitting further
bank_train$train_test <- "train"
bank_test$train_test <- "test"

# Combining both datasets
bank_dataset <- rbind(bank_train, bank_test)
cat("The train set has ", dim(bank_train)[1], "rows and ", dim(bank_train)[2], "columns, ")
cat("The test set has ", dim(bank_test)[1], "rows and ", dim(bank_test)[2], "columns, ")
cat("The combined dataset has ", dim(bank_dataset)[1], "rows and ", dim(bank_dataset)[2], "columns")

```

#### NA Discovery
We need to clean NA values in all the columns and fill the empty cells with proper judgements based on each variable's condition.
First, we explore which columns have missing values.

```{r NA Discovery}
# Visualizing Missing Data
plot_missing(bank_dataset) + theme_minimal()

na.cols <- which(colSums(is.na(bank_dataset)) > 0)
paste('There are', length(na.cols), 'columns with missing values')
sort(colSums(sapply(bank_dataset[na.cols], is.na)), decreasing = TRUE)

```

Therefore no missing values are present in the dataset and we can continue with feature engineering

#### Data Structure
Now we will check the structure of the dataset.
```{r Dataset Structure and Features}
# visualizing the dataset to know the structure and components of each variable
str(bank_dataset)
summary(bank_dataset)
```

#### EDA

```{r Target Variable}

# Count of target classes
table(bank_dataset$y)

#Determine Class Proportions
class_percentage <- bank_dataset[bank_dataset$train_test == "train",] %>% group_by(y) %>% summarise(count = n(), percentage = round(n()*100/36168,2))

#Barplot of Classes
ggplot(class_percentage, aes(x=y, y=count, label=count, fill = y)) + 
  geom_bar(stat='identity') + 
  labs(title="Proportions of Classes in the Training Set",subtitle = "",caption = "Source: Group 4",
       x = "Class", y= "Count", fill = "Subscribe") + theme_classic() + 
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  scale_fill_manual(values = c("tomato3", "seagreen4"))


#Pie Chart of Classes
ggplot(class_percentage, aes(x = "", y = percentage, fill = y)) +
  geom_bar(width = 1, stat = "identity", color = "gray55") +
  coord_polar("y", start = 0) +
  geom_text(aes(y = sum(percentage) - cumsum(percentage) + percentage / 2, label = percentage), color = "black", size = 5) +
  theme_minimal() + ggtitle("Percentage of each class") + labs(x="", y="", fill = "Subscribe", caption = "Source: Group 4") + scale_fill_manual(values = c("tomato3", "seagreen4"))

```


```{r Job}
# JOB
# Count for each job versus the target variable 
table(bank_train$job, bank_train$y)

# Count of each category in the whole dataset
ggplot(data = bank_dataset, aes(x = job)) + geom_bar(fill = "seagreen4") + theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + labs(x = "Job", y = "Count", caption = "Source: Group 4")

# Probability table
job <- as.data.frame(prop.table(table(bank_train$job, bank_train$y)))
colnames(job) <-  c("job", "y", "perc")

ggplot(data = job, aes(x = job, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Job")+
    ylab("Percent") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

# Using count
job2 <- as.data.frame(table(bank_train$job, bank_train$y))
colnames(job2) <-  c("job", "y", "count")

ggplot(data = job2, aes(x = job, y = count, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Job")+
    ylab("Count") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

```

```{r Marital}
# Marital Status
# Count for each marital status versus the target variable 
table(bank_dataset$marital)
table(bank_train$marital, bank_train$y)

# Count of each category in the whole dataset
ggplot(data = bank_dataset, aes(x = marital)) + geom_bar(fill = "seagreen4") + theme_minimal() + labs(x = "Marital Status", y = "Count", caption = "Source: Group 4")

# Probability table
marital <- as.data.frame(prop.table(table(bank_train$marital, bank_train$y)))
colnames(marital) <-  c("marital", "y", "perc")

ggplot(data = marital, aes(x = marital, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Marital")+
    ylab("Percent") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

# Using count
marital2 <- as.data.frame(table(bank_train$marital, bank_train$y))
colnames(marital2) <-  c("marital", "y", "count")

ggplot(data = marital2, aes(x = marital, y = count, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Marital")+
    ylab("Count") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")
```


```{r Age}
# Age distribution
ggplot(bank_dataset, aes(age)) + geom_density(fill = "seagreen4") + theme_minimal() + labs(x = "Age", y = "Density", caption = "Source: Group 4")

# We will bin the age into age groups and visualize it with subscribtions
bank_dataset <- bank_dataset %>% mutate(age_group = ifelse(age >= 18 & age <= 25, "18-25",
                                                           ifelse(age > 25 & age <= 35, "26-35",
                                                                  ifelse(age > 35 & age < 50, "36-49",
                                                                         ifelse(age >= 50 & age <= 65, "50-65", ">65")))))
# Count of each category in the whole dataset
ggplot(data = bank_dataset, aes(x = age_group)) + geom_bar(fill = "seagreen4") + theme_minimal() + labs(x = "Age Group", y = "Count", caption = "Source: Group 4")



# Probability table
age_group <- as.data.frame(prop.table(table(bank_dataset[bank_dataset$train_test=="train",]$age_group, bank_dataset[bank_dataset$train_test=="train",]$y)))
colnames(age_group) <-  c("age_group", "y", "perc")

ggplot(data = age_group, aes(x = age_group, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Age Group")+
    ylab("Percent") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

# Using count
age_group2 <- as.data.frame(table(bank_dataset[bank_dataset$train_test=="train",]$age_group, bank_dataset[bank_dataset$train_test=="train",]$y))
colnames(age_group2) <-  c("age_group", "y", "count")

ggplot(data = age_group2, aes(x = age_group, y = count, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Age Group")+
    ylab("Count") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

```

```{r Education}

# Education Level
# Count for each educational level versus the target variable 
table(bank_dataset$education)
table(bank_dataset[bank_dataset$train_test=="train",]$education, bank_dataset[bank_dataset$train_test=="train",]$y)

# Count of each category in the whole dataset
ggplot(data = bank_dataset, aes(x = education)) + geom_bar(fill = "seagreen4") + theme_minimal() + labs(x = "Education", y = "Count", caption = "Source: Group 4")

# Probability table
edu <- as.data.frame(prop.table(table(bank_dataset[bank_dataset$train_test=="train",]$education, bank_dataset[bank_dataset$train_test=="train",]$y)))
colnames(edu) <-  c("education", "y", "perc")

ggplot(data = edu, aes(x = education, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Education")+
    ylab("Percent") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

# Using count
edu2 <- as.data.frame(table(bank_dataset[bank_dataset$train_test=="train",]$education, bank_dataset[bank_dataset$train_test=="train",]$y))
colnames(edu2) <-  c("education", "y", "count")

ggplot(data = edu2, aes(x = education, y = count, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Education")+
    ylab("Count") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

```



```{r Default}

# Default: has credit in default? (categorical: 'no', 'yes', 'unknown')

table(bank_dataset$default)
table(bank_dataset[bank_dataset$train_test=="train",]$default, bank_dataset[bank_dataset$train_test=="train",]$y)

# Count of each category in the whole dataset
ggplot(data = bank_dataset, aes(x = default)) + geom_bar(fill = "seagreen4") + theme_minimal() + labs(x = "default", y = "Count", caption = "Source: Group 4")

# Probability table
default <- as.data.frame(prop.table(table(bank_dataset[bank_dataset$train_test=="train",]$default, bank_dataset[bank_dataset$train_test=="train",]$y)))
colnames(default) <-  c("default", "y", "perc")

ggplot(data = default, aes(x = default, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("default")+
    ylab("Percent") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

# Using count
default2 <- as.data.frame(table(bank_dataset[bank_dataset$train_test=="train",]$default, bank_dataset[bank_dataset$train_test=="train",]$y))
colnames(default2) <-  c("default", "y", "count")

ggplot(data = default2, aes(x = default, y = count, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Default")+
    ylab("Count") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

```


```{r Housing}

# Housing: has housing loan? (categorical: 'no', 'yes', 'unknown')

table(bank_dataset$housing)
table(bank_dataset[bank_dataset$train_test=="train",]$housing, bank_dataset[bank_dataset$train_test=="train",]$y)

# Count of each category in the whole dataset
ggplot(data = bank_dataset, aes(x = housing)) + geom_bar(fill = "seagreen4") + theme_minimal() + labs(x = "housing", y = "Count", caption = "Source: Group 4")

# Probability table
housing <- as.data.frame(prop.table(table(bank_dataset[bank_dataset$train_test=="train",]$housing, bank_dataset[bank_dataset$train_test=="train",]$y)))
colnames(housing) <-  c("housing", "y", "perc")

ggplot(data = housing, aes(x = housing, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Housing")+
    ylab("Percent") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

# Using count
housing2 <- as.data.frame(table(bank_dataset[bank_dataset$train_test=="train",]$housing, bank_dataset[bank_dataset$train_test=="train",]$y))
colnames(housing2) <-  c("housing", "y", "count")

ggplot(data = housing2, aes(x = housing, y = count, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Housing")+
    ylab("Count") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

```

```{r Loan}

# Loan: has personal loan? (categorical: 'no', 'yes', 'unknown')

table(bank_dataset$loan)
table(bank_dataset[bank_dataset$train_test=="train",]$loan, bank_dataset[bank_dataset$train_test=="train",]$y)

# Count of each category in the whole dataset
ggplot(data = bank_dataset, aes(x = loan)) + geom_bar(fill = "seagreen4") + theme_minimal() + labs(x = "loan", y = "Count", caption = "Source: Group 4")

# Probability table
loan <- as.data.frame(prop.table(table(bank_dataset[bank_dataset$train_test=="train",]$loan, bank_dataset[bank_dataset$train_test=="train",]$y)))
colnames(loan) <-  c("loan", "y", "perc")

ggplot(data = loan, aes(x = loan, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Loan")+
    ylab("Percent") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

# Using count
loan2 <- as.data.frame(table(bank_dataset[bank_dataset$train_test=="train",]$loan, bank_dataset[bank_dataset$train_test=="train",]$y))
colnames(loan2) <-  c("loan", "y", "count")

ggplot(data = loan2, aes(x = loan, y = count, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Loan")+
    ylab("Count") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

```


```{r Duration}

# Duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if duration=0 then y='no'). Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input should only be included for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.


# Duration distribution
ggplot(bank_dataset, aes(duration)) + geom_density(fill = "seagreen4") + theme_minimal() + labs(x = "Duration", y = "Density", caption = "Source: Group 4")
ggplot(bank_dataset, aes(duration)) + geom_histogram(fill = "seagreen4") + theme_minimal() + labs(x = "Duration", y = "Count", caption = "Source: Group 4")

min(bank_dataset$duration)
max(bank_dataset$duration)

# We will group durations to see if call duration has an effect on the probability of subscribtion
# We will bin the age into age groups and visualize it with subscribtions
bank_dataset <- bank_dataset %>% mutate(duration_group = ifelse(duration >= 0 & duration <= 500, "Very Short",
                                                           ifelse(duration > 500 & duration <= 1500, "Short",
                                                                  ifelse(duration > 1500 & duration < 3000, "Long", "Very Long"
                                                                         ))))

# Count of each category in the whole dataset
ggplot(data = bank_dataset, aes(x = duration_group)) + geom_bar(fill = "seagreen4") + theme_minimal() + labs(x = "Call Duration", y = "Count", caption = "Source: Group 4")



# Probability table
duration_group <- as.data.frame(prop.table(table(bank_dataset[bank_dataset$train_test=="train",]$duration_group, bank_dataset[bank_dataset$train_test=="train",]$y)))
colnames(duration_group) <-  c("duration_group", "y", "perc")

ggplot(data = duration_group, aes(x = duration_group, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Call Duration")+
    ylab("Percent") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

# Using count
duration_group2 <- as.data.frame(table(bank_dataset[bank_dataset$train_test=="train",]$duration_group, bank_dataset[bank_dataset$train_test=="train",]$y))
colnames(duration_group2) <-  c("duration_group", "y", "count")

ggplot(data = duration_group2, aes(x = duration_group, y = count, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Call Duration")+
    ylab("Count") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

ggplot(bank_dataset[bank_dataset$train_test=="train",], aes(x=y, y=duration)) +
  geom_boxplot(fill='seagreen4', color="tomato3") + labs(x = "Subscribe", y = "Call Duration", caption = "Source: Group 4") + theme_minimal()

```

```{r Campaign}
# campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)
table(bank_dataset$campaign)

ggplot(bank_dataset, aes(campaign)) + geom_histogram(fill = "seagreen4") + theme_minimal() + labs(x = "Campaign", y = "Count", caption = "Source: Group 4")
ggplot(bank_dataset, aes(campaign)) + geom_density(fill = "seagreen4") + theme_minimal() + labs(x = "Campaign", y = "Density", caption = "Source: Group 4")

bank_dataset <- bank_dataset %>% mutate(campaign_group = ifelse(campaign >= 0 & campaign <= 10, "1-10",
                                                           ifelse(campaign > 10 & campaign <= 20, "11-20",
                                                                  ifelse(campaign > 20 & campaign <= 30, "21-30",
                                                                         ifelse(campaign > 30 & campaign <= 40, "31-40",
                                                                                ifelse(campaign > 40 & campaign <= 50, "41-50", "> 50"))
                                                                         ))))


# Count of each category in the whole dataset
ggplot(data = bank_dataset, aes(x = campaign_group)) + geom_bar(fill = "seagreen4") + theme_minimal() + labs(x = "Campaign", y = "Count", caption = "Source: Group 4") + scale_x_discrete(limits = c("1-10", "11-20", "21-30", "31-40", "41-50", ">50"))

# Probability table
campaign_group <- as.data.frame(prop.table(table(bank_dataset[bank_dataset$train_test=="train",]$campaign_group, bank_dataset[bank_dataset$train_test=="train",]$y)))
colnames(campaign_group) <-  c("campaign_group", "y", "perc")

ggplot(data = campaign_group, aes(x = campaign_group, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Campaign")+
    ylab("Percent") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

# Using count
campaign_group2 <- as.data.frame(table(bank_dataset[bank_dataset$train_test=="train",]$campaign_group, bank_dataset[bank_dataset$train_test=="train",]$y))
colnames(campaign_group2) <-  c("campaign_group", "y", "count")

ggplot(data = campaign_group2, aes(x = campaign_group, y = count, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("Call campaign")+
    ylab("Count") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

ggplot(bank_dataset[bank_dataset$train_test=="train",], aes(x=y, y=campaign)) +
  geom_boxplot(fill='seagreen4', color="tomato3") + labs(x = "Subscribe", y = "Campaign", caption = "Source: Group 4") + theme_minimal()

```
```{r poutcome}
# poutcome: outcome of the previous marketing campaign (categorical: 'failure','nonexistent','success')
table(bank_dataset$poutcome)
table(bank_dataset[bank_dataset$train_test=="train",]$poutcome, bank_dataset[bank_dataset$train_test=="train",]$y)

# Count of each category in the whole dataset
ggplot(data = bank_dataset, aes(x = poutcome)) + geom_bar(fill = "seagreen4") + theme_minimal() + labs(x = "poutcome", y = "Count", caption = "Source: Group 4")

# Probability table
poutcome <- as.data.frame(prop.table(table(bank_dataset[bank_dataset$train_test=="train",]$poutcome, bank_dataset[bank_dataset$train_test=="train",]$y)))
colnames(poutcome) <-  c("poutcome", "y", "perc")

ggplot(data = poutcome, aes(x = poutcome, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("poutcome")+
    ylab("Percent") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

# Using count
poutcome2 <- as.data.frame(table(bank_dataset[bank_dataset$train_test=="train",]$poutcome, bank_dataset[bank_dataset$train_test=="train",]$y))
colnames(poutcome2) <-  c("poutcome", "y", "count")

ggplot(data = poutcome2, aes(x = poutcome, y = count, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +xlab("poutcome")+
    ylab("Count") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_manual(values = c("tomato3", "seagreen4")) + labs(fill = "Subscribe", caption = "Source: Group 4")

```

```{r previous}
# previous: number of contacts performed before this campaign and for this client (numeric)

```

```{r pdays}
# pdays: number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously contacted)

```


#### Data Cleaning

#### Feature Creation

```{r}

```


#### Feature Elimination

```{r}
str(bank_dataset)
```


#### Factorizing Features

```{r}

```


#### Outliers 

```{r}

```


#### Scaling

```{r}

```


#### Final Dataset

#### Train and Test Split
```{r Train test validation split}
# Split the dataset into TRAIN and TEST
training_data <- as.data.frame(bank_dataset[bank_dataset$train_test == "train",])
test_data <- as.data.frame(bank_dataset[bank_dataset$train_test == "test",])

# # need to drop "TBD" from the target variable as TBD should be predicted for TEST dataset
# training_data$status_group <- droplevels(training_data$status_group)
# 
# # Remove the "dataType" column from TRAIN, VALIDATION and TEST dataset
# training_data <- training_data[,-which(names(dataset) == "dataType")]
# test_data <- test_data[,-which(names(dataset) == "dataType")]
```

#### Modeling
##### Logistic Regression
##### Decision Trees
##### XGB
##### Random Forest
##### KNN




